The Linguistic Landscape of Stream-of-Consciousness Literature

### 2024-04-04 paper/paper.qmd
update title

# Calculate the word frequency over all unique words and bind all frequency rate of authors together to conduct a comparative comparison
# Code sourced from https://medium.com/the-data-nudge/nlp-basics-exploring-word-frequency-with-the-tidytext-r-package-ac35a6d805f4

>>>>

# Calculate the word frequency over all unique words and bind all frequency rate of authors together to conduct a comparative comparison
# Code referenced from https://medium.com/the-data-nudge/nlp-basics-exploring-word-frequency-with-the-tidytext-r-package-ac35a6d805f4
